\documentclass[12pt,english]{article}

\input{preamble_package}
% Citation comes loading other packages, so that footnotes follow biblatex-chicago style
\input{preamble_citation}

% Responses to Referees
\usepackage{blindtext}
\newcommand{\aptxspc}{1.8}
\newcommand{\rrquote}{1.1}
\newcommand{\rrxspc}{1.5}

\begin{document}

% SUBMISSION COVER
\thispagestyle{empty}
\begingroup
  \doublespacing
  \centering
  \LARGE REVISE \& RESUBMIT SUBMISSION\\[0.25em]
  \LARGE Journal of Policy Analysis and Management \\[0.25em]
  \LARGE MANUSCRIPT ID: JPAM-2025-13688 \\[1.0em]
\endgroup
This document and the associated contents in the accepted version of JPAM-2025-13688 for the Journal of Policy Analysis and Management. I include:
\begin{enumerate}
    \item Title page information
    \begin{itemize}
        \item Title and Author
        \item Abstract
        \item Keywords
        \item Acknowledgment
    \end{itemize}
    \item The manuscript
    \begin{itemize}
        \item Main manuscript text
        \item Main manuscript references
        \item Main manuscript figures
        \item Main manuscript tables
    \end{itemize}  
    \item \hyperref[r&r:responses]{Responses to the editor and referees comments}
    \item The online appendix, which is separately paged. It includes an online appendix title page, appendix A, appendix B, appendix C, and references for citations in the appendix.
\end{enumerate}
\clearpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Part I. Title Page, Authors, Abstract, etc. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Load in title page information, title, author information, abstract, etc are stored here
\input{manuscript_title_etc}
\pagenumbering{roman}
\setcounter{page}{1}

% Part I.a.1 Title
\section*{TITLE AND AUTHORS}
\subsection*{TITLE AND RUNNING HEAD}
\begin{itemize}[label={}, leftmargin=*]
    \item Title: \textbf{\PAPERTITLE}
    \item Running Head:  \textbf{Bias and Asian Identity}
\end{itemize}
% Part I.a.2 Author info
\subsection*{AUTHORS}
\begin{itemize}[label={}, leftmargin=*]
    \item List of authors:
    \begin{enumerate}
        \item \AUTHORHADAHINFO
    \end{enumerate}
    \item Corresponding author:
    \begin{itemize}
        \item \textbf{\AUTHORHADAHINFO}
    \end{itemize}
\end{itemize}

\subsection*{Data Availability Statement}
The data that support the findings of this study will be openly available to all researchers after the review process. For immediate information regarding the data and/or computer programs used for this study, please contact Hussain Hadah at hhadah@tulane.edu.

\subsection*{Funding Statement}

The author has no funding for the research, authorship, and/or publication of this article to report.

\subsection*{Conflict of Interest Disclosure}
The author declare that they have no conflicts of interest regarding the publication of this manuscript.

\clearpage 

% Part I.b Abstract
\doublespacing
\section*{ABSTRACT}
% \begin{myRaggedRight}
\PAPERABSTRACT
% \end{myRaggedRight}
\clearpage 

% Part I.c Keywords
\doublespacing
\section*{KEYWORDS}
\PAPERKEYWORDS
\clearpage 

% Part IV.d Acknowledgements
\doublespacing
\section*{ACKNOWLEDGMENT}
% \begin{myRaggedRight}
\ACKNOWLEDGMENTS
% \end{myRaggedRight}
\clearpage 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Part II. Manuscript main text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand*{\thefootnote}{\arabic{footnote}}
\begingroup
  \centering
  \Large MANUSCRIPT TEXT\\[1em]
\endgroup
% Manuscript main text
% \begin{myRaggedRight}
\input{manuscript_main}
% \end{myRaggedRight}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Part III. Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\begingroup
\setstretch{1.0}
\setlength\bibitemsep{5.0pt}
\printbibliography[title=References for Manuscript]
\endgroup
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Part IV. Tables and figures
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{manuscript_tab_fig}

\clearpage 
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PART V. Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\begin{refsection}

% reset page numbers
\pagenumbering{arabic}
\setcounter{page}{1}
\end{refsection}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PART VI. Responses to Editor and Referees
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{refsection}
% Reset section numbering
\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\Alph{section}.\arabic{subsection}.\arabic{subsubsection}}

        \section{Responses to Editors and Referee} \label{r&r:responses}
        \begin{spacing}{\rrxspc}
            I would like to thank the editors and the anonymous referees for their insightful comments, suggestions, and effort and time in reviewing this paper. I have addressed all the comments and suggestions in the revised manuscript. Below, I provide a summary of the changes made to the manuscript in response to the comments and suggestions. Please note that the comments from the referees are quoted verbatim, and my responses follow each comment.
        \end{spacing}

    \newpage
    
    \section{Responses to the Editor}
        I would like to thank the editor for the suggestions and comments. Below is a detailed response to the comments and suggestions.
        \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{E1: } 1. Reviewer 1 is satisfied with the revisions and notes only one minor edit, which I agree should be addressed.
            \end{quotation}
        \end{spacing}
        \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{E1: } 2. Reviewer 2 also acknowledges that the paper has improved substantially but recommends several additional revisions to further strengthen it. I
                believe these suggestions are reasonable and would enhance the manuscript. With respect to Reviewer 2’s final point, this could likely be addressed by
                examining the interaction between bias and income. While you present interaction effects with parental education in the Appendix, I recommend
                including the interaction with income in the main text.
            \end{quotation}
        \end{spacing}
        \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}
            
    \section{Responses to Referee One}
        I would like to thank referee one for the insightful comments and suggestions. Below is a my response to the referee's comment.
    
    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R1: } 1. One minor point remains. For the sake of transparency and clarity, I would recommend that the author explicitly list the ANES survey items used to
                measure racial animus (e.g., whether these are measures of ethnocentrism, racial resentment, feeling thermometers, or a combination thereof).
                Including this information in a footnote or appendix would be sufficient. Provided that this information is added in the final version, I support
                conditional acceptance of the manuscript as is.
            \end{quotation}
        \end{spacing}
        \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}
    \clearpage
    \pagebreak

    \section{Responses to Referee Two}
    I would like to thank referee two for the insightful and constructive comments and suggestions. Below is a detailed response to the comments and suggestions.

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 1. The paper is too constrained by its history. It should show quickly that when all measured ancestors are Asian, individuals almost always report
                themselves to be Asian, but when at least one parent or grandparent is not Asian, a substantial fraction identify as something other than solely Asian,
                leaving room for other factors to influence their choice of identity. Note that saying they identify as non-Asian is misleading. Kamala Harris identifies as
                both black and Indian, not as non-Indian or non-black.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 2. Since almost all individuals born in (East) Asia or with two Asian parents identify as Asian, there is little point in trying to explain who identifies this way. In fact, finding large effects of anti-Asian sentiment on this group detracts from the story because it makes us wonder how you can find two-digit effects on a group that is roughly 96% Asian in identify. This group should simply be dropped.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 3. Having set up the paper with this background, you should skip the binary choice models and move straight to the multinomial logit. This is where all
                the interesting results are located.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 4. You should be much more careful about significance. The fact that one effect is statistically significant and the other is not does not mean that they are statistically significantly different. Very few of, for example, your WA - AW differences are statistically significant. If there is a coherent story that is
                supported by the point estimates, it may be worth pointing out that the point estimates are suggestive. Otherwise, it probably makes sense to say, the
                WA-AW estimates were not statistically significant. Therefore, you combined them into a single mixed-race category.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 5. The resulting paper would be much more streamlined and cohesive and substantially shorter.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 6. The paper continues to be inconsistent about the interaction between identity and income differentials. The introduction says that “if individuals respond to prejudice by avoiding Asian racial identification, conventional analyses of racial gaps may systematically underestimate
                disparities in the most prejudiced areas.” Unless we know the effect of income interacted with prejudice, the effect could go in either direction, or there
                could be no effect. Similarly, “identity choices may influence measured labor market trajectories among racial groups, potentially making Asian
                American integration appear more successful than reality suggests,” is a statement about the effect of income on identity in different generations.
                Moreover, if this is the motivation for the paper, the lack of any analysis of the magnitude of the effect on the estimated income of Asians in the U.S. is
                disappointing, to say the least.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 7. I take it that other forms of mixed race (e.g. black/Asian) were too small to include.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \begin{spacing}{\rrxspc}
            \begin{quotation}
                \textbf{R2: } 8. Figures 2A and 3 are not reassuring. There are large changes within states that strike me as implausible. If there really are large changes, it should be possible to control for state fixed effects. I assume the author would have controlled for state fixed effects if that did not render the coefficients too imprecise to be useful.
            \end{quotation}
    \end{spacing}
    \begin{spacing}{\rrxspc}
        \textbf{Response:} 
    \end{spacing}

    \clearpage
    \pagebreak

    \end{refsection}

\clearpage
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PART VII. Online Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{refsection}
% Reset section numbering
\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\Alph{section}.\arabic{subsection}.\arabic{subsubsection}}

% Title Page for Appendix
% special footnote symbols
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begingroup
\doublespacing
\centering
\Large ONLINE APPENDIX \\[1.5em]
\LARGE \PAPERTITLE \\[0.75em]
\large
\AUTHORHADAH\footnote[1]{\AUTHORHADAHINFO}\\[1.0em]
\endgroup
\clearpage

% Online appendix
\input{manuscript_online_appendix}

\newpage
\pagebreak

% Appendix Bibliography
\begingroup
\setstretch{1.0}
\setlength\bibitemsep{0pt}
\printbibliography[title=References for Online Appendix]
\endgroup
\pagebreak
\end{refsection}

\end{document}